The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-12 paper/discussion.tex
paper: wordsmithing

Ignoring these complications, in this work we showed that
binarity does bias transit survey occurrence rates, simply through its 
effects on the number of searchable stars and the apparent radii of detected 
planets.
Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
might lead to underestimate HJ rates by a multiplicative factor of $\approx 
1.3$.

We assess the effect this might have towards resolving the hot Jupiter rate 
discrepancy by asking:
what is the probability of Wright et al. (2012)'s result, given a rate drawn 
from the stated bounds of Petigura et al. (in prep)? (See 
Table~\ref{tab:hj_rates}).
In other words, we first take the true HJ rate as $\Lambda_{\rm HJ} = 5.7 \pm 
1.3$, with Gaussian uncertainties, and then drawing from a Poisson 
distribution compute the probability of detecting at least 10 hot Jupiters in 
a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for Guo et al. 
(2017)'s measured metallicity difference between the {\it Kepler}\ field and 
the local solar neighborhood, 9\% of RV surveys would detect at least 10 hot 
Jupiters.
If we then multiply again by $1.3$ to account for binarity's bias, we find that
23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
would be quite teneous.
We emphasize that this result is only suggestive~--~a true resolution of the 
rate discrepancy would likely require a detailed understanding of the {\it 
Kepler}\ field's multiplicity statistics.

>>>>

Ignoring these complications, in this work we showed that
binarity does bias transit survey occurrence rates, simply through its 
effects on the number of searchable stars and the apparent radii of detected 
planets.
Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
could lead to underestimated HJ rates by a multiplicative factor of $\approx 
1.3$.

We assess the effect this might have towards resolving the hot Jupiter rate 
discrepancy by asking:
what is the probability of Wright et al. (2012)'s result, given a rate drawn 
from the stated bounds of Petigura et al. (in prep)? (See 
Table~\ref{tab:hj_rates}).
In other words, we first take the true HJ rate as $\Lambda_{\rm HJ} = 5.7 \pm 
1.3$, with Gaussian uncertainties, and then drawing from a Poisson 
distribution compute the probability of detecting at least 10 hot Jupiters in 
a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for Guo et al. 
(2017)'s measured metallicity difference between the {\it Kepler}\ field and 
the local solar neighborhood, 9\% of RV surveys would detect at least 10 hot 
Jupiters.
If we then multiply again by $1.3$ to account for binarity's bias, we find that
23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
would be quite tenuous
We emphasize that this result is only suggestive~--~a true resolution of the 
rate discrepancy would likely require a detailed understanding of the {\it 
Kepler}\ field's multiplicity statistics.
